Explore Vegetation Data

### 2016-02-16 explore_veg_data.Rmd
Update overstory species list.
Changed species ID 'arma' to genus ID 'arcto' for overstory species data.

alt_species <- rbind(alt_sp_2005, alt_sp_2014)
write.csv(alt_species, "analysis/data/alt-species-dbh-corrected.csv", row.names = F)
```

>>>>

alt_species <- rbind(alt_sp_2005, alt_sp_2014)
sort(unique(alt_species$species))
alt_species[alt_species=="arma"] <- "arcto"
write.csv(alt_species, "analysis/data/alt-species-dbh-corrected.csv", row.names = F)
```
